\section{zkSNARK overview}
zkSNARK is a type of cryptographic proof protocol that reveal no information about the knowledge we try to prove. Here is the meaning of each letters.
\begin{itemize}
    \item ZK for zero knowledge, the user's informations still remain confidential without compromising the security.
    \item S for succint, the test of the proof is supposed to be fast, with a small size.
    \item N for non-interactive, there is no constant interaction, communication or exchange between the prover and the verifier. 
    \item ARK for argument of knowledge, the prover want to show to the verifier that he knows some knowledge.
\end{itemize}
A protocol should satisfy the 3 cores properties we defined above for zero-knowledge proof. \\

To construct the proof zkSNARK use polynomials evaluation, the idea is to convert our problem into a "Rank-1 Constraint System" \textbf{R1CS}. Then we convert the R1CS in a "Quadratic Arithmetic Circuit" (\textbf{QAP}) defined below with Lagrange interpolation. After that we evaluate our equation system on a point and check the equality. 

\textbf{Quadratic Arithmetic Circuit (QAP)} is a representation of an arithmetic circuit. 
If we have Q an arithmetic circuit that compute something with $a_{1...l}$ the outputs and inputs of the circuit, and  $a_{l+1...m}$ the witness of the circuit (i.e the intermediate values). 
A QAP is a triplet set of polynomials $\{A_i[X]$, $B_i[X]$, $C_i[X]\}_{i=0}^m$, each $A_i$, $B_i$, $C_i$ are of degree n, such that \[ (\sum_{i=0}^m a_i A_i) (\sum_{i=0}^m a_i B_i) = \sum_{i=0}^m a_i C_i  \] 
\\ Now considering our QAP defined above with an n-degree polynomial Z[X] we say this accept a vector $x \in F^n$ such that Z(x) divide our equation above. If we have our set of polynomials $\{A_i[X]$, $B_i[X]$, $C_i[X]\}_{i=0}^m$ we can find Z with this method : 
\\ Generate an arbitrary set of n points $S \subseteq F$. Construct A(x), B(x), C(x) in such a way that $A(s_i ), B(s_i ), C(s_i )$ are the i-th rows of A, B, C respectively. The Z(x) is defined in such a way that
$\forall s \in S : Z(s) = 0$.
\\ Then we have : \[ (\sum_{i=0}^m a_i A_i(x)) * (\sum_{i=0}^m a_i B_i(x)) = \sum_{i=0}^m a_i C_i(x) \bmod Z(x) \] 
\\ See \cite{Succinct_Non_Interactive_Arguments_from_Quadratic_Arithmetic_Programs} for more explanations. \\
This two websites give a good example of how each transformations are done \cite{QAP_creation} and \cite{QAP_creation_2}.